\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-08-14 doc/sui14/iteration1.tex
update demographics

\subsection{Method}
We deployed 10 wireless nodes in an indoor environment (Figure~\ref{fig:targeting-study-layout}), each with a number ID and a letter representing the name. For the study, we recruited \changes{16} participants from our institution \changes{(8 males and 6 females)} \changes{using email invitations}. Figure X shows their department distribution. \sean{will calculate later. shall we use a pie chart?}  \changes{14} had never used Google Glass before, so we offered a tutorial before the experiment in order to introduce the device. Four participants wore prescription glasses, which makes Glass more cumbersome to use and adjust and may have affected their task performance. In this study, the IR LED was fixed and not repositionable as shown in Figure~\ref{fig:glass}.

>>>>

\subsection{Method}
We deployed 10 wireless nodes in an indoor environment (Figure~\ref{fig:targeting-study-layout}), each with a number ID and a letter representing the name. For the study, we recruited \changes{16} participants from our institution \changes{(8 males and 6 females)} \changes{using email invitations}. \changes{They are composed of undergrad students, graduate students, and university staff. Their background ranges from Information(6), Engineering(4), Math and Science(4), Design(1), Others(1)}  \changes{14} had never used Google Glass before, so we offered a tutorial before the experiment in order to introduce the device. Four participants wore prescription glasses, which makes Glass more cumbersome to use and adjust and may have affected their task performance. In this study, the IR LED was fixed and not repositionable as shown in Figure~\ref{fig:glass}.
